\begin{abstract}
Assurance cases are used to demonstrate confidence in system properties of interest (e.g. for safety and/or security). 
A number of approaches for constructing assurance case are adopted by industries in the safety-critical domain. 
However, the task of constructing assurance cases remain a manual, lengthy and informal process. 
%Thus, model based approaches have been proposed to promote automation.
The Structured Assurance Case Metamodel (SACM) is a standard specified by the Object Management Group (OMG). 
SACM is designed to be used to construct assurance case models. 
However, the adoption of SACM faces challenges as its intended usage has not been sufficiently explained. 
In addition, there has not been support to interoperate between existing assurance case models (such as Goal Structuring Notation models) and SACM models.
SACM provides a solid foundation for model-based system assurance, which bears great application potentials in growing technology domains such as autonomous systems, Cyber-Physical Systems (CPS) and Internet of Things (IoT). 

In this paper, we provide a definitive guide to explain the intended usage of SACM. We also explains the relationship between existing assurance cases and SACM models. 
In addition, to promote model based approach, we provide a SACM compliant metamodel for the Goal Structuring Notation (GSN) and the transformation between GSN and SACM.
We propose a systematic approach for model based system assurance using SACM, in the sense that all corresponding information can be bridged together using the facilities provided in SACM.
We also discuss briefly the application of model-based system assurance in the context of CPS and networks of CPSs.

\keywords{Mode Driven Engineering, Structured Assurance Case Metamodel, Model Based System Assurance, Goal Structuring Notation}
\end{abstract}
